Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-08-01 emsoft-2019/camera_ready/Cont_Syn.tex
last updates

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily,escapeinside={<@}{@>}]
 model = input() 
 $\Delta$ = input()
 $\varepsilon_{Q}$ = input()
 assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
 $\varepsilon$ = $\varepsilon_{A/D}$ + $\varepsilon_{Q}$<@$\quad$//\,\,width of the tube@>

@@

%\subsection{Algorithm}
\autoref{lst:alg} shows a high-level view of our optimization algorithm for
implementing robust MPC controllers with guaranteed error bounds.

Given a state-space model of a plant (line 1), our algorithm returns four matrices
$\hat{F}$, $\hat{G}$, $\hat{H}$, and $\hat{K}$,
which soundly implement a robust explicit MPC controller in mixed-precision
fixed-point arithmetic.
Our algorithm takes two additional inputs, $\Delta$ and $\varepsilon_Q$ (line 2, 3). 
The disturbance $\Delta$ provided by the user represents a starting point for 
the search for a robust controller. In principle, the user can set $\Delta = 0$,
however note that the finite-precision implementation of the controller will always
incur at least some small error. In practice we thus start the search with a slightly
larger value, e.g. $\Delta = 0.1$. Our algorithm will perform a linear search and
increase $\Delta$ if needed.

@@

\smallskip
\noindent
\textbf{Termination of the algorithm.}
From a theoretical point of view, the error due to a wrong region selection does not necessarily converge since each new designed controller may differ from the previous ones. Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated. However, by rewriting \autoref{eq:RMPC_prob}, we have
\begin{align*}
\nu_0(x_0, \Delta),\ldots&,\nu_{N-1}(x_0,\Delta)=\\
\mathrm{argmin} & \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
\quad  \text{s.t.} \quad & x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad \quad & u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad \quad & u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\}.
%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
\end{align*}
Assuming the optimization has a unique solution for every $\Delta$, 
one may use the results on continuity of the $\mathrm{argmin}$ function to compute an upper bound on the 
Lipschitz constant of the optimal input $\nu = \kappa(x)$ in Equation~\eqref{eq:affine_map} that holds for all $\Delta$. 
The computed bound will only depend on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used 
to evaluate the maximum error over incorrect region selection. 
This bound can be quite large, leading to a very conservative bound on the maximum number of iterations before convergence. 
From an experimental point of view, our observations show that for our range of parameters $\varepsilon_{\mathit{SAFE}}$, convergence was
always reached after only a few iterations.

\smallskip
\noindent
\textbf{Computational complexity.} 
It is shown in \cite{Alessio2009} that the number of regions $P$ 
in Equation~\eqref{eq:affine_map} is upper bounded by $2^q$, where $q$ is the total number of constraints in \autoref{eq:RMPC_prob}.
Assuming that each region has at most $N$ hyperplanes, computation of the incorrect region selection error requires at 
most $i\times N\times 2^q$ affine computations, where $i$ denotes the number of times the RMPC design updates $\Delta$ before convergence. 
In our experiments, the computation of the incorrect region selection error takes only a few minutes for our largest tested benchmarks. 
The complexity of the precision tuning is linear with respect to the number of regions and hyperplanes. 
So, $(P+ N\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
In each encoding, the uniform-precision detection %takes linear number of steps \RM{in what parameter?} before convergence. 
%It 
starts from 1-bit and increases the precision one by one until the first valid configuration. 
The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, 
and bounded by $n^2$ in the worst case, where $n$ is the number of variables. \RM{how is $n$ related to the other parameters?}

% In case the conditional in line 9 succeeds, the precision tuning phase starts. The way we do the precision tuning is the following: we provide in input to Daisy a numerical error-bound together with an expression to quantize (e.g. an activation function). Daisy returns in output both the minimal-uniform precision, and the mixed-precision configuration, such that the quantization of the expression in the given precision configuration introduces an error that is bounded by the input error.

% In line 10 we compute the error bound for approximate control output error. This is going to be the maximal error we tolerate for activation functions. The precision tuning at line 11 receives in input the approximation control error together with the coefficients F and G. In Line 12 we give to Daisy the error $\varepsilon$ for borders, together with the hyperplanes coefficients H and K.

%\eva{The precision tuning, which is the main contribution of the paper is not explained.}

>>>>

\begin{figure}
\begin{lstlisting}[language=Python,numbers=left,numbersep=3pt,frame=lines,keepspaces=true,mathescape=true,basicstyle=\small\ttfamily,escapeinside={<@}{@>}]
 model = input() 
 $\Delta$ = input()
 $\varepsilon_{Q}$ = input()
 assert ($\Delta$ >= 0 and $\varepsilon_{Q}$ > 0)
$\varepsilon$ = $\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}$$\quad$//width of the tube

@@

%\subsection{Algorithm}
\autoref{lst:alg} shows a high-level view of our optimization algorithm for
implementing robust MPC controllers with guaranteed error bounds.
Given a state-space model of a plant (line 1), our algorithm returns four matrices
$\hat{F}$, $\hat{G}$, $\hat{H}$, and $\hat{K}$,
which soundly implement a robust explicit MPC controller in mixed-precision
fixed-point arithmetic.
Our algorithm takes two additional inputs, $\Delta$ and $\varepsilon_Q$ (line 2, 3). 
The disturbance $\Delta$ provided by the user represents a starting point for 
the search for a robust controller. In principle, the user can set $\Delta = 0$,
however note that the finite-precision implementation of the controller will always
incur at least some small error. In practice we thus start the search with a slightly
larger value, e.g. $\Delta = 0.1$. Our algorithm will perform a linear search and
increase $\Delta$ if needed.

@@

\smallskip
\noindent
\textbf{Termination of the algorithm.}
From a theoretical point of view, the error due to a wrong region selection does not necessarily converge since each new designed controller may differ from the previous ones. Therefore, it is not easy to give an upper bound over the number of times that the robust MPC design needs to be repeated. However, by rewriting \autoref{eq:RMPC_prob}, we have
\begin{align*}
\nu_0(x_0, \Delta),\ldots&,\nu_{N-1}(x_0,\Delta)=\\
\mathrm{argmin} & \max_{w_0,\cdots,w_{N-1}} \sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i) + x_N^TQ_Fx_N\nonumber\\
\quad  \text{s.t.} \quad & x_{i+1}=Ax_i+Bu_i + E w_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad \quad & u_i=\mu x_i+v_i, \quad\forall i\in\{0,1,\cdots,N-1\}\nonumber\\
\quad \quad & u_i\in\mathcal{U},x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W}_{\Delta},\,\,\forall i\in\{0,1,\cdots,N\}.
%&x_i\in\mathcal{X},\quad \forall w_i\in\mathcal{W},\quad\forall i\in\{0,1,\cdots,N\},
\end{align*}
Assuming the optimization has a unique solution for every $\Delta$, 
one may use the results on continuity of the $\mathrm{argmin}$ function to compute an upper bound on the 
Lipschitz constant of the optimal input $\nu = \kappa(x)$ in Equation~\eqref{eq:affine_map} that holds for all $\Delta$. 
The computed bound will only depend on the dynamics of the system depicted in \autoref{eq:DSS} and hence can be used 
to evaluate the maximum error over incorrect region selection. 
This bound can be quite large, leading to a very conservative bound on the maximum number of iterations before convergence. 
From an experimental point of view, our observations show that for reasonable range of parameters, convergence was
always reached after only a few iterations.

\begin{comment}
\RM{I took out the following section because it was too hacky. The complexity should be given in terms of the original
problem input, but we keep inventing new parameters. Also, $n$ below in the complexity of mixed precision tuning doesn't make
sense. In case we bring this back, it should be fixed.}
\smallskip
\noindent
\textbf{Computational complexity.} 
It is shown in \cite{Alessio2009} that the number of regions $P$ 
in Equation~\eqref{eq:affine_map} is upper bounded by $2^q$, where $q$ is the total number of constraints in \autoref{eq:RMPC_prob}.
Assuming that each region has at most $N$ hyperplanes, computation of the incorrect region selection error requires at 
most $i\times N\times 2^q$ affine computations, where $i$ denotes the number of times the RMPC design updates $\Delta$ before convergence. 
In our experiments, the computation of the incorrect region selection error takes only a few minutes for our largest tested benchmarks. 
The complexity of the precision tuning is linear with respect to the number of regions and hyperplanes. 
So, $(P+ N\times P)$ is an upper bound for the number of problems we need to encode in Daisy.
In each encoding, the uniform-precision detection %takes linear number of steps \RM{in what parameter?} before convergence. 
%It 
starts from 1-bit and increases the precision one by one until the first valid configuration. 
The complexity of mixed-precision tuning with delta-debugging is $n\times log(n)$ in average, 
and bounded by $n^2$ in the worst case, where $n$ is the number of variables. \RM{how is $n$ related to the other parameters?}

\end{comment}

### 2019-08-01 emsoft-2019/camera_ready/Error_Analysis.tex
last updates

The first part of the error in~\autoref{eq:delta} captures the error due to
selecting of the incorrect region.
This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats. In order to quantify the error, we define the expanded border $\bar{\mathcal B}_{ij}$ as the tube around the border between the regions $\mathcal{R}_i$ and $\mathcal{R}_j$:
% \begin{equation*}
% \bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
% \end{equation*}
% for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values. The norm is also applied element-wise to the entries of the matrices.

\begin{equation*}
\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
\end{equation*}
where $\varepsilon$ captures the uncertainty in computing the correct region.
%
The width of the tube $\varepsilon$ is due to two sources of errors:
analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
bounds in memory $\varepsilon_{Q}$:
\begin{equation}\label{eq:epsilontot}
  \varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
\end{equation}

While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
\begin{equation}\label{eq:quantizationlines}
  \varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
\end{equation}
where $\hat{x}$ is the finite-precision value of $x$.
%\eva{For which index is this evaluated, $i$, $j$ or both?}
That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
($\hat{H}_{p}$ and $\hat{K}_{p}$).
This second error can be tuned providing a trade-off between accuracy and
memory storage required.

% Note that $\mathcal R_i\subset \bar{\mathcal R}_i$. In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
% Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.   
% $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$ that include all states in $\mathcal R_i$this definition expands the regions $\mathcal $
 %That is, with infinite-precision arithmetic
 Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
 the expanded borders:
 \label{eq:maximization}
 \max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|

@@

 	\Mahmoud{\begin{itemize}

@@

 	We define the fixed point realization of the controller in \autoref{eq:affine_map} as:

@@

 	 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}

@@

 	 	\varepsilon=\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}

@@

% 	\Mahmoud{We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
% 	\label{eq:affine_map_hat}
% 	\hat\kappa(\hat x_k)=
% 	\begin{cases}
% 	\hat F_1\hat x_k+\hat G_1 & \text{if $\hat x_k\in \mathcal{\hat R}_1$}\\
% 	\hat F_2\hat x_k+\hat G_2 & \text{if $\hat x_k\in \mathcal{\hat R}_2$}\\
% 	\vdots\\
% 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}
% 	\end{cases} 
% 	where $\hat x_k$ denotes the output of the analog-to-digital converter corresponding to the input $x_k$. Further, $\hat F_i, \hat G_i$ denote the fixed point representations corresponding to $F_i, G_i$ and $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\,|\, \hat H_i\hat x\leq \hat K_i\}$.}
%	\Mahmoud{Let us define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$. Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i,i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i,i=1,2,\ldots, P\}$, where $\hat F_i$, $\hat G_i$, $\hat H_i$ and $\hat K_i$ denote the fixed point representations corresponding to $F_i$, $G_i$, $H_i$ and $K_i$, respectively. }
% 	\begin{equation}\label{eq:epsilontot1}
 	Analog conversion happens just before the controller receives the sensor input from the plant
 	and is given by:
 	\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
 	where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
 	is the number of bits available to quantize the analog signal, and $2^{r}$ is
 	the resolution of the converter.\\
 	While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
 	$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
 	\begin{equation}\label{eq:quantizationlines}
 	\varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
 	where $\hat{x}$ is the finite-precision value of $x$.
 	%\eva{For which index is this evaluated, $i$, $j$ or both?}
 	That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
 	precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
 	($\hat{H}_{p}$ and $\hat{K}_{p}$).
 	This second error can be tuned providing a trade-off between accuracy and
 	memory storage required.
 	Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
 	the expanded borders:
 	\label{eq:maximization}
 	\max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
 	% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|

@@

The incorrect region error (\autoref{eq:maximization}) is computed with Matlab.

Since $v_{i}-v_{j}$ is also affine, and because we defined the tube as a convex region 
surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of contraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
For each computed vertex $v_i$, we compute a $n$-dimensional
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.

@@

\RM{what about the following commented-out comment of Sadegh?}
\begin{comment}
\textcolor{red}{Sadegh: This is long comment on the content of this section. I cannot figure out how this line of reasoning is mapped to the implementation. We can discard my comment given that we are close to the deadline.}

>>>>

%\subsection{Incorrect Region Selection}
%The first part of the error in~\autoref{eq:delta} captures the error due to
%selecting of the incorrect region.
%This would happen since the matrices $H_i,K_i$ are stored in the hardware with fixed-point formats. In order to quantify the error, we define the expanded border $\bar{\mathcal B}_{ij}$ as the tube around the border between the regions $\mathcal{R}_i$ and $\mathcal{R}_j$:
%% \begin{equation*}
%% \bar{\mathcal R}_i := \bigcup_{\hat H_i,\hat K_i} \left\{x\in\mathbb R^n\,|\,\hat H_i x\le \hat K_i, \|H_i-\hat H_i\|\le \epsilon_f,\|K_i-\hat K_i\|\le \epsilon_f\right\}
%% \end{equation*}
%% for $i\in\{1,2,\ldots, P\}$, where $\epsilon_f$ is the maximum error of using fixed-point format instead of the precise values. The norm is also applied element-wise to the entries of the matrices. 
%\begin{equation*}
%\bar{\mathcal B}_{ij} := \left\{x\in\mathbb R^n\,|\, \| H_i x - K_i\| \le \varepsilon\,\, \text{ and }\,\, \| H_j x - K_j\| \le \varepsilon \right\},
%\end{equation*}
%where $\varepsilon$ captures the uncertainty in computing the correct region.
%%
%The width of the tube $\varepsilon$ is due to two sources of errors:
%analog-to-digital conversion $\varepsilon_{A/D}$ and the quantization of region
%bounds in memory $\varepsilon_{Q}$:
%\begin{equation}\label{eq:epsilontot}
%\end{equation}
%Analog conversion happens just before the controller receives the sensor input from the plant
%and is given by:
%\begin{equation*}
%\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
%\end{equation*}
%where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
%is the number of bits available to quantize the analog signal, and $2^{r}$ is
%the resolution of the converter.
%While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
%$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
%\begin{equation}\label{eq:quantizationlines}
%  \varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
%\end{equation}
%where $\hat{x}$ is the finite-precision value of $x$.
%%\eva{For which index is this evaluated, $i$, $j$ or both?}
%That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
%precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
%($\hat{H}_{p}$ and $\hat{K}_{p}$).
%This second error can be tuned providing a trade-off between accuracy and
%memory storage required.
%% Note that $\mathcal R_i\subset \bar{\mathcal R}_i$. In other words, $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$.
%% Note that $\bar{\mathcal R}_i\cap \bar{\mathcal R}_j$ gives us the states where one of the two regions $\mathcal R_i, \mathcal R_i$ might be selected instead of the other one because of the fixed-precision implementation of the regions.   
%% $\bar{\mathcal R}_i$ is the expanded version of $\mathcal R_i$ that include all states in $\mathcal R_i$this definition expands the regions $\mathcal $
% %That is, with infinite-precision arithmetic
% Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
% the expanded borders:
% \label{eq:maximization}
% \max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
%% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|

@@

@@

 	We define the fixed point realization of the controller in \autoref{eq:affine_map} as

@@

 	 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}.

@@

 	 	\varepsilon=\max_i \{||F_i||_2\}\varepsilon_{A/D}+\varepsilon_{Q}.

@@

% 	\Mahmoud{We define the fixed point realization of the controller in \autoref{eq:affine_map} as:
% 	\begin{equation}
% 	\label{eq:affine_map_hat}
% 	\hat\kappa(\hat x_k)=
% 	\begin{cases}
% 	\hat F_1\hat x_k+\hat G_1 & \text{if $\hat x_k\in \mathcal{\hat R}_1$}\\
% 	\hat F_2\hat x_k+\hat G_2 & \text{if $\hat x_k\in \mathcal{\hat R}_2$}\\
% 	\vdots\\
% 	\hat F_P x_k+\hat G_P & \text{if $ \hat x_k\in \mathcal{\hat R}_P$}
% 	\end{cases} 
% 	\end{equation}
% 	where $\hat x_k$ denotes the output of the analog-to-digital converter corresponding to the input $x_k$. Further, $\hat F_i, \hat G_i$ denote the fixed point representations corresponding to $F_i, G_i$ and $\mathcal{\hat R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal{\hat R}_i= \{ \hat x\in\mathcal X\,|\, \hat H_i\hat x\leq \hat K_i\}$.}
%
%	\Mahmoud{Let us define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$. Similarly, we define $\hat{\mathcal H}:= \{\hat H_i,\hat K_i,i=1,2,\ldots, P\}$ and $\hat{\mathcal F}:=\{\hat F_i,\hat G_i,i=1,2,\ldots, P\}$, where $\hat F_i$, $\hat G_i$, $\hat H_i$ and $\hat K_i$ denote the fixed point representations corresponding to $F_i$, $G_i$, $H_i$ and $K_i$, respectively. }
%
% 	\begin{equation}\label{eq:epsilontot1}
% 	\varepsilon=\varepsilon_{A/D}+\varepsilon_{Q}
% 	\end{equation}
 	%
 	%
 	Analog conversion happens just before the controller receives the sensor input from the plant
 	and is given by:
 	\begin{equation*}
 	\varepsilon_{A/D}=\frac{V_{cc}}{2^{r}-1}
 	\end{equation*}
 	where $V_{cc}$ is the reference voltage of the converter (e.g. typically 5V), $r$
 	is the number of bits available to quantize the analog signal, and $2^{r}$ is
 	the resolution of the converter.\\
 	While $\varepsilon_{A/D}$ is intrinsic to the capabilities of the device,
 	$\varepsilon_{Q}$ depends on the precision used to store the boundaries:
 	\begin{equation}\label{eq:quantizationlines}
 	\varepsilon_{Q} \ge  \|(H_i - \hat{H}_i) \hat{x} + (K_i - \hat{K}_i)\|, \quad \forall \hat{x},\forall i,
 	\end{equation}
 	where $\hat{x}$ is the finite-precision value of $x$.
 	%\eva{For which index is this evaluated, $i$, $j$ or both?}
 	That is, $\varepsilon_{Q}$ bounds the distance between any hyperplane in infinite
 	precision ($H$ and $K$ matrices), and its counter-part quantized by $p$ bits 
 	($\hat{H}$ and $\hat{K}$).
 	This second error can be tuned providing a trade-off between accuracy and
 	memory storage required.
 	Therefore, the first term in~\autoref{eq:delta} can be computed less conservatively by maximizing only over 
 	the expanded borders:
 	\begin{equation}
 	\label{eq:maximization}
 	\max_{x,i,j}\{\|F_ix+G_i-F_jx-G_j\|,\,x\in \bar{\mathcal B}_{ij}\}.
 	% \max_{\forall i,j.\mathit{neighbor}(\mathcal{R}_{i},\mathcal{R}_{j})}&|F_{i}\statevar+G_{i} - (F_{j}\statevar+G_{j})|
 	\end{equation}

@@

The incorrect region error (\autoref{eq:maximization}) is computed with Matlab. Since $v_{i}-v_{j}$ is also affine, and because we defined the tube as a convex region 
surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of constraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
For each computed vertex $v_i$, we compute a $n$-dimensional
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.

@@

%\RM{what about the following commented-out comment of Sadegh?}
\begin{comment}
\textcolor{red}{Sadegh: This is long comment on the content of this section. I cannot figure out how this line of reasoning is mapped to the implementation. We can discard my comment given that we are close to the deadline.}
